---
title: "data_structure"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = TRUE,
                      cache.lazy = TRUE,
                      warn = -1)
source("data_structure_functions.R")
library(tibble)
library(data.table)
library(tidyverse)
library(microbenchmark)
library(dplyr)
library(ggplot2)
library(memuse)
library(lobstr)

# list which store the differents instances' size
num_elem <- c(1000,10000,100000)
options(warn=-1)
```

# I. Introduction 

In order to boost the program, we want to use a datatype structure that is light and robust, in 
order to contains the model's inputs (USMS).
What will follow in this document are the tests done in the purpose of determining the best datatype
structure suited for that.
The tests will concern the generation speed, the memory weight and the manipulation ease.

## I.A The Dataypes structures

Initially, they were 6 candidates :

- The List type
- The Reference Class type
- The DataFrame type
- The DataTable type
- The Tibble type
- The Matrix type

However, the Matrix type was the first one to be put away because it can only contains informations
with homogenous types (e.g only numeric or character but not numeric and character together). Or, an
USM is composed of :

- a name (character)
- a beginning date (numeric)
- an ending date (numeric)
- an initialisation file name (character)
- the ground name (character)
- a station file name (character)
- a first climate file name (character)
- a second climate file name (character)
- the year of culture (numeric)
- the number of plants (numeric)
- the simulation_code (numeric)
- informations about the first plant (3 informations(fplt,ftec,flai)) (character)
- informations about the second plant (same)
- the observation file name (character)

So here are examples of usm in the remaining datatypes.

### I.A.1 List

```{r example usm list}

example_usm_list <- usm_list("usm_1","sol_canne")
example_usm_list

```

### I.A.2 Class

```{r example usm class}
example_usm_class <- usm_class("usm_1","sol_canne")
example_usm_class

```

### I.A.3 DataFrame

```{r example usm dataframe}

example_usm_dataframe <- usm_dataframe("usm_1","sol_canne")
example_usm_dataframe

```

### I.A.4 DataTable

```{r example usm datatable}

example_usm_datatable <- usm_datatable("usm_1","sol_canne")
example_usm_datatable

```

### I.A.5 Tibble

```{r example usm tibble}

example_usm_tibble <- usm_tibble("usm_1","sol_canne")
example_usm_tibble

```

# II. Tests

The firsts tests to be made were instanciation tests. We tested the instanciation time and weight
for each datatype structure with different instanciation method and for differents sizes (10 000,
100 000, 1 000 000)

## II.A Instanciation Tests

### II.A.1 List Vs Class

These tests were made for list and class types because only these two types can be instanciated
with a non pre-allocated method, which is not possible for the other types.

```{r list vs class, echo=FALSE}
load("List_Vs_Class_times.RData")
load("List_Vs_Class_weights.RData")

df <- bench_list2df(benchmarks_list_class)
time_unit = paste("median_log10_",df$unit[1],sep="")

df_npa_list <- dplyr::filter(df,doe <= 3,expr == "NPA_Lapply")
df_pa_list <- dplyr::filter(df,doe <= 3, expr == "PA_Lapply")
df_weights_list <- dplyr::filter(df_weights_list_class, type == "List")

df_npa_class <- dplyr::filter(df,doe > 3, expr == "NPA_Lapply")
df_pa_class <- dplyr::filter(df,doe > 3, expr == "PA_Lapply")
df_weights_class <- dplyr::filter(df_weights_list_class, type == "Class")

list_npa <- data.frame(Usms = num_elem, Valeurs = log10(df_npa_list$median), type = "Non Pre-Allocated List")
list_pa <- data.frame(Usms = num_elem, Valeurs = log10(df_pa_list$median), type = "Pre-Allocated List")

df_list <- rbind(list_npa,list_pa)
cat("List time graph for 1K Usms to 100K Usms")
ggplot(df_list)+geom_line(aes(Usms,Valeurs,colour=type))+labs(y = time_unit)

class_npa <- data.frame(Usms = num_elem,Valeurs = log10(df_npa_class$median), type = "Non pre-Allocated Class")
class_pa <- data.frame(Usms = num_elem,Valeurs = log10(df_pa_class$median), type = "Pre-Allocated Class")

df_class <- rbind(class_npa,class_pa)
cat("Class time graph for 1K Usms to 100K Usms")
ggplot(df_class)+geom_line(aes(Usms,Valeurs,colour=type))+labs(y = time_unit)

weights_list <- data.frame(Usms = num_elem,Valeurs = log10(df_weights_list$Valeurs), type = "List")
weights_class <- data.frame(Usms = num_elem,Valeurs = log10(df_weights_class$Valeurs), type = "Class")

df_weights <- rbind(weights_class,weights_list)
cat("Weights graph between List and Class")
ggplot(df_weights)+geom_line(aes(Usms,Valeurs,colour=type))+labs(y = "log10_bytes")

df_final <- rbind(list_npa,class_npa)
cat("Comparative time graph for fastest instanciation method for List and Class")
ggplot(df_final)+geom_line(aes(Usms,Valeurs,colour=type))+labs(y = time_unit)
```

Even, if the NPA instanciation is 'lighter' than the others, its huge instanciation time makes that we will not use it. Indeed, during the tests, we must divide by hundred the number of usm the NPA contains because it will last more tha 3 days before it creates a 1M usms structure. 

### II.A.2 DataFrame, DataTable and Tibble

Now, let's move on to the tests involving the DataFrame,DataTable and Tibble instanciation methods.
Indeed, they are severals ways to instanciate each of these types. 
DataFrame : By affecting list in a dataframe's row or by row binding a list of dataframe.
DataTable : Doing the same as before but for a DataTable or by casting the DataFrame output into a 
DataTable.
Tibble : Same ways as for DataTable

``` {r df,dt,tb, echo=FALSE}
load("Df_Vs_Dt_Vs_Tb_times.RData")
load("Df_Vs_Dt_Vs_Tb_weights.RData")

df <- bench_list2df(benchmarks_df_dt_tb)
time_unit = paste("median_log10_",df$unit[1],sep="")

df_itself <- dplyr::filter(df,doe < 4,expr == "name1")
df_lapply <- dplyr::filter(df,doe < 4,expr == "name2" )
df_weights <- weights_df_dt_tb[1,]

dt_itself <- dplyr::filter(df,doe > 3,doe < 7,expr == "name1")
dt_lapply <- dplyr::filter(df,doe > 3,doe < 7,expr == "name2")
dt_weights <- weights_df_dt_tb[2,]

tb_itself <- dplyr::filter(df,doe > 6,expr == "name1")
tb_lapply <- dplyr::filter(df,doe > 6,expr == "name2")
tb_weights <- weights_df_dt_tb[3,]

itself_df <- data.frame(Usms = num_elem, Valeurs = log10(df_itself$median), type = "Dataframe itself")
lapply_df <- data.frame(Usms = num_elem, Valeurs = log10(df_lapply$median), type = "Dataframe lapply")
weights_df <- data.frame(Usms = num_elem, Valeurs = log10(df_weights), type = "Dataframe")

itself_dt <- data.frame(Usms = num_elem, Valeurs = log10(dt_itself$median), type = "Datatable itself")
lapply_dt <- data.frame(Usms = num_elem, Valeurs = log10(dt_lapply$median), type = "Datatable lapply")
weights_dt <- data.frame(Usms = num_elem, Valeurs = log10(dt_weights), type = "Datatable")

itself_tb <- data.frame(Usms = num_elem, Valeurs = log10(tb_itself$median), type = "Tibble itself")
lapply_tb <- data.frame(Usms = num_elem, Valeurs = log10(tb_lapply$median), type = "Tibble lapply")
weights_tb <- data.frame(Usms = num_elem, Valeurs = log10(tb_weights), type = "Tibble")

cat("Time graph for Dataframe for 1K USms to 100K USms")
final_df <- rbind(itself_df,lapply_df)
ggplot(final_df)+geom_line(aes(Usms,Valeurs,colour=type))+labs(y = time_unit)

cat("Time graph for Datatable for 1K USms to 100K USms")
final_dt <- rbind(itself_dt,lapply_dt)
ggplot(final_dt)+geom_line(aes(Usms,Valeurs,colour=type))+labs(y = time_unit)

cat("Time graph for Tibble for 1K USms to 100K USms")
final_tb <- rbind(itself_tb,lapply_tb)
ggplot(final_tb)+geom_line(aes(Usms,Valeurs,colour=type))+labs(y = time_unit)

cat("Weights graph betweend Dataframe, Datatable and Tibble")
final_weights <- rbind(weights_df,weights_dt,weights_tb)
ggplot(final_weights)+geom_line(aes(Usms,Valeurs,colour=type))+labs(y = "log10_bytes")

cat("Comparative time graph for the fastest instanciation method for DataFrame, DataTable and Tibble")
final_times <- rbind(lapply_df,lapply_dt,lapply_tb)
ggplot(final_times)+geom_line(aes(Usms,Valeurs,colour=type))+labs(y = time_unit)
```

We can see that the DataTable type seems to be faster to instanciate. Furthermore, it has exactly the same weight as the others types.

## II.B Most suitable datatype structure

With the previous results, we now try to find the most suitable datatype.

```{r best datatype structure, echo=FALSE}
best_weights <- rbind(weights_list,weights_dt)
cat("Weights graph between List and DataTable")
ggplot(best_weights)+geom_line(aes(Usms,Valeurs,colour=type))+labs(y = "log10_bytes")

cat("Comparative time graph for the fastest instanciation method for List and DataTable")
best_times <- rbind(list_npa,lapply_dt)
ggplot(best_times)+geom_line(aes(Usms,Valeurs,colour=type))+labs(y = time_unit)
```
  
We can conclude that the most suitable datatype is one of DataFrame,DataTable and Tibble.

# III. Extraction

We're now moving to Usm sublist extraction test part. For this part, we tested two ways of extracting usms sublist, by random usm name and criteria research. Each tests was tested in several ways.

## III.A Random extraction by Usm name

In these tests we're randomly picking and extracting usm names.

```{r random extraction,echo=FALSE}
load("random_extract.RData")

df <- bench_list2df(benchmarks)
time_unit = paste("median_log10_",df$unit[1],sep="")

basic_li <- dplyr::filter(df,expr == "random_extract_for_usm_list_class(li, random_names)")
basic_cla <- dplyr::filter(df,expr == "random_extract_for_usm_list_class(cla, random_names)")
mapped_li <- dplyr::filter(df,expr == "map_random_extract(li, random_names)")
mapped_cla <- dplyr::filter(df,expr == "map_random_extract(cla, random_names)")
basic_df <- dplyr::filter(df,expr == "random_extract_for_usm_df_dt_tb(df, random_names)")
basic_dt <- dplyr::filter(df,expr == "random_extract_for_usm_df_dt_tb(df, random_names)")
basic_tb <- dplyr::filter(df,expr == "random_extract_for_usm_df_dt_tb(df, random_names)")

li <- data.frame(Usms = num_elem, Valeurs = log10(basic_li$median), type = "Basic extract List")
cla <- data.frame(Usms = num_elem, Valeurs = log10(basic_cla$median), type = "Basic extract Class")
map_li <- data.frame(Usms = num_elem, Valeurs = log10(mapped_li$median), type = "Map extract List")
map_cla <- data.frame(Usms = num_elem, Valeurs = log10(mapped_cla$median), type = "Map extract Class")
df <- data.frame(Usms = num_elem, Valeurs = log10(basic_df$median), type = "Basic extract Dataframe")
dt <- data.frame(Usms = num_elem, Valeurs = log10(basic_dt$median), type = "Basic extract Datatable")
tb <- data.frame(Usms = num_elem, Valeurs = log10(basic_tb$median), type = "Basic extract Tibble")

cat("Graph time comparison between the differents ways to extract data and the differents structures")
extract_plot <- rbind(li,cla,map_li,map_cla,df,dt,tb)
ggplot(extract_plot)+geom_line(aes(Usms,Valeurs,colour=type))+labs(y = time_unit)
```

## III.B Extraction by criteria

In these tests we're selectionning a usm's criteria and extracting the usm in which the criteria is present.

```{r criteria extraction,echo=FALSE}
load("Criteria_extract.RData")

df <- bench_list2df(benchmarks)
time_unit = paste("median_log10_",df$unit[1],sep="")

basic_li <- dplyr::filter(df,expr == 'criteria_extract_for_usm_list_class(li, "ground_name", "sol_canne")')
basic_cla <- dplyr::filter(df,expr == 'criteria_extract_for_usm_list_class(cla, "ground_name", "sol_canne")')
mapped_li <- dplyr::filter(df,expr == 'map_criteria_extract(li, "ground_name", "sol_canne")')
mapped_cla <- dplyr::filter(df,expr == 'map_criteria_extract(cla, "ground_name", "sol_canne")')
basic_df <- dplyr::filter(df,expr == 'criteria_extract_for_usm_df_dt_tb(df, "ground_name", "sol_canne")')
basic_dt <- dplyr::filter(df,expr == 'criteria_extract_for_usm_df_dt_tb(dt, "ground_name", "sol_canne")')
basic_tb <- dplyr::filter(df,expr == 'criteria_extract_for_usm_df_dt_tb(tb, "ground_name", "sol_canne")')

li <- data.frame(Usms = num_elem, Valeurs = log10(basic_li$median), type = "Basic extract List")
cla <- data.frame(Usms = num_elem, Valeurs = log10(basic_cla$median), type = "Basic extract Class")
map_li <- data.frame(Usms = num_elem, Valeurs = log10(mapped_li$median), type = "Map extract List")
map_cla <- data.frame(Usms = num_elem, Valeurs = log10(mapped_cla$median), type = "Map extract Class")
df <- data.frame(Usms = num_elem, Valeurs = log10(basic_df$median), type = "Basic extract Dataframe")
dt <- data.frame(Usms = num_elem, Valeurs = log10(basic_dt$median), type = "Basic extract Datatable")
tb <- data.frame(Usms = num_elem, Valeurs = log10(basic_tb$median), type = "Basic extract Tibble")

cat("Graph time comparison between the differents ways to extract data and the differents structures")
extract_plot <- rbind(li,cla,map_li,map_cla,df,dt,tb)
ggplot(extract_plot)+geom_line(aes(Usms,Valeurs,colour=type))+labs(y = time_unit)
```

# IV.Conclusion